### 2009-08-07 doc/latex/cowichan__defaults_8hpp.tex
Re-generated doxygen with linuxtuples additions.

\#define \hyperlink{cowichan__defaults_8hpp_30524c594b6941ca7822489d1794813b}{ALL\_\-NR}~15000

@@

\#define \hyperlink{cowichan__defaults_8hpp_85076a3092aabd0bc4661e9184e2ddf3}{ALL\_\-NC}~15000

@@

\#define \hyperlink{cowichan__defaults_8hpp_e36abbd26bf4ea979de0b63b1a37e349}{ALL\_\-N}~15000

@@

\#define \hyperlink{cowichan__defaults_8hpp_02f3c90de37aa6314330a7e0cb68a1f5}{LIFE\_\-ITERATIONS}~10

@@

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Defaults for \hyperlink{class_cowichan}{Cowichan} programs.

\subsection{Define Documentation}
\hypertarget{cowichan__defaults_8hpp_e36abbd26bf4ea979de0b63b1a37e349}{
\index{cowichan\_\-defaults.hpp@{cowichan\_\-defaults.hpp}!ALL\_\-N@{ALL\_\-N}}
\index{ALL\_\-N@{ALL\_\-N}!cowichan_defaults.hpp@{cowichan\_\-defaults.hpp}}
\subsubsection[{ALL\_\-N}]{\setlength{\rightskip}{0pt plus 5cm}\#define ALL\_\-N~15000}}
\label{cowichan__defaults_8hpp_e36abbd26bf4ea979de0b63b1a37e349}

Default matrix size for square matrices for all problems. \hypertarget{cowichan__defaults_8hpp_85076a3092aabd0bc4661e9184e2ddf3}{
\index{cowichan\_\-defaults.hpp@{cowichan\_\-defaults.hpp}!ALL\_\-NC@{ALL\_\-NC}}
\index{ALL\_\-NC@{ALL\_\-NC}!cowichan_defaults.hpp@{cowichan\_\-defaults.hpp}}
\subsubsection[{ALL\_\-NC}]{\setlength{\rightskip}{0pt plus 5cm}\#define ALL\_\-NC~15000}}
\label{cowichan__defaults_8hpp_85076a3092aabd0bc4661e9184e2ddf3}

Default number of columns for rectangular matrices for all problems. \hypertarget{cowichan__defaults_8hpp_30524c594b6941ca7822489d1794813b}{
\index{cowichan\_\-defaults.hpp@{cowichan\_\-defaults.hpp}!ALL\_\-NR@{ALL\_\-NR}}
\index{ALL\_\-NR@{ALL\_\-NR}!cowichan_defaults.hpp@{cowichan\_\-defaults.hpp}}
\subsubsection[{ALL\_\-NR}]{\setlength{\rightskip}{0pt plus 5cm}\#define ALL\_\-NR~15000}}
\label{cowichan__defaults_8hpp_30524c594b6941ca7822489d1794813b}

@@

Default number of rows for invperc. \hypertarget{cowichan__defaults_8hpp_02f3c90de37aa6314330a7e0cb68a1f5}{
\index{cowichan\_\-defaults.hpp@{cowichan\_\-defaults.hpp}!LIFE\_\-ITERATIONS@{LIFE\_\-ITERATIONS}}
\index{LIFE\_\-ITERATIONS@{LIFE\_\-ITERATIONS}!cowichan_defaults.hpp@{cowichan\_\-defaults.hpp}}
\subsubsection[{LIFE\_\-ITERATIONS}]{\setlength{\rightskip}{0pt plus 5cm}\#define LIFE\_\-ITERATIONS~10}}
\label{cowichan__defaults_8hpp_02f3c90de37aa6314330a7e0cb68a1f5}

>>>>

\#define \hyperlink{cowichan__defaults_8hpp_30524c594b6941ca7822489d1794813b}{ALL\_\-NR}~1000

@@

\#define \hyperlink{cowichan__defaults_8hpp_85076a3092aabd0bc4661e9184e2ddf3}{ALL\_\-NC}~1000

@@

\#define \hyperlink{cowichan__defaults_8hpp_e36abbd26bf4ea979de0b63b1a37e349}{ALL\_\-N}~1000

@@

\#define \hyperlink{cowichan__defaults_8hpp_02f3c90de37aa6314330a7e0cb68a1f5}{LIFE\_\-ITERATIONS}~3

@@

\subsection{Detailed Description}
Defaults for \hyperlink{class_cowichan}{Cowichan} programs.

\subsection{Define Documentation}
\hypertarget{cowichan__defaults_8hpp_e36abbd26bf4ea979de0b63b1a37e349}{
\index{cowichan\_\-defaults.hpp@{cowichan\_\-defaults.hpp}!ALL\_\-N@{ALL\_\-N}}
\index{ALL\_\-N@{ALL\_\-N}!cowichan_defaults.hpp@{cowichan\_\-defaults.hpp}}
\subsubsection[{ALL\_\-N}]{\setlength{\rightskip}{0pt plus 5cm}\#define ALL\_\-N~1000}}
\label{cowichan__defaults_8hpp_e36abbd26bf4ea979de0b63b1a37e349}

Default matrix size for square matrices for all problems. \hypertarget{cowichan__defaults_8hpp_85076a3092aabd0bc4661e9184e2ddf3}{
\index{cowichan\_\-defaults.hpp@{cowichan\_\-defaults.hpp}!ALL\_\-NC@{ALL\_\-NC}}
\index{ALL\_\-NC@{ALL\_\-NC}!cowichan_defaults.hpp@{cowichan\_\-defaults.hpp}}
\subsubsection[{ALL\_\-NC}]{\setlength{\rightskip}{0pt plus 5cm}\#define ALL\_\-NC~1000}}
\label{cowichan__defaults_8hpp_85076a3092aabd0bc4661e9184e2ddf3}

Default number of columns for rectangular matrices for all problems. \hypertarget{cowichan__defaults_8hpp_30524c594b6941ca7822489d1794813b}{
\index{cowichan\_\-defaults.hpp@{cowichan\_\-defaults.hpp}!ALL\_\-NR@{ALL\_\-NR}}
\index{ALL\_\-NR@{ALL\_\-NR}!cowichan_defaults.hpp@{cowichan\_\-defaults.hpp}}
\subsubsection[{ALL\_\-NR}]{\setlength{\rightskip}{0pt plus 5cm}\#define ALL\_\-NR~1000}}
\label{cowichan__defaults_8hpp_30524c594b6941ca7822489d1794813b}

@@

Default number of rows for invperc. \hypertarget{cowichan__defaults_8hpp_02f3c90de37aa6314330a7e0cb68a1f5}{
\index{cowichan\_\-defaults.hpp@{cowichan\_\-defaults.hpp}!LIFE\_\-ITERATIONS@{LIFE\_\-ITERATIONS}}
\index{LIFE\_\-ITERATIONS@{LIFE\_\-ITERATIONS}!cowichan_defaults.hpp@{cowichan\_\-defaults.hpp}}
\subsubsection[{LIFE\_\-ITERATIONS}]{\setlength{\rightskip}{0pt plus 5cm}\#define LIFE\_\-ITERATIONS~3}}
\label{cowichan__defaults_8hpp_02f3c90de37aa6314330a7e0cb68a1f5}

### 2009-08-07 doc/latex/cowichan__mpi_2sort_8hpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{cowichan__mpi_2sort_8cpp}{
\section{cowichan\_\-mpi/sort.cpp File Reference}
\label{cowichan__mpi_2sort_8cpp}\index{cowichan\_\-mpi/sort.cpp@{cowichan\_\-mpi/sort.cpp}}
}
Implementation of MPI sorting algorithms.

{\tt \#include \char`\"{}sort.hpp\char`\"{}}\par
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__mpi}{cowichan\_\-mpi}
\begin{CompactList}\small\item\em Additional classes and functions specific to mpi implementation. \item\end{CompactList}

\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__mpi_7f82c459ad086060228b2bd8100bf9c7}{cowichan\_\-mpi::getNumRemainingNodes} (const mpi::communicator \&world, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} level)
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__mpi_a7c14e0bec9c9da1d56a348c9a0cf1f8}{cowichan\_\-mpi::power2} (\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} n)
\item 
void \hyperlink{namespacecowichan__mpi_4ab537d0df99e9011b206c7259e82d35}{cowichan\_\-mpi::quick\_\-sort} (const mpi::communicator \&world, \hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} level, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} owner)
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__mpi_83904b95f448398ff15331182ee0c007}{cowichan\_\-mpi::quick\_\-sort\_\-partition} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} pivotIndex)
\end{CompactItemize}

\subsection{Detailed Description}
Implementation of MPI sorting algorithms.

>>>>

\hypertarget{cowichan__mpi_2sort_8hpp}{
\section{cowichan\_\-mpi/sort.hpp File Reference}
\label{cowichan__mpi_2sort_8hpp}\index{cowichan\_\-mpi/sort.hpp@{cowichan\_\-mpi/sort.hpp}}
}
Sorting algorithms that use MPI.

{\tt \#include \char`\"{}cowichan\_\-mpi.hpp\char`\"{}}\par
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__mpi}{cowichan\_\-mpi}
\begin{CompactList}\small\item\em Additional classes and functions specific to mpi implementation. \item\end{CompactList}

\end{CompactItemize}
\subsection*{Defines}
\begin{CompactItemize}
\item 
\#define \hyperlink{cowichan__mpi_2sort_8hpp_b3aee1394b5864d458c40b7878acbe83}{QUICK\_\-SORT\_\-CUTOFF}~100
\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__mpi_7f82c459ad086060228b2bd8100bf9c7}{cowichan\_\-mpi::getNumRemainingNodes} (const mpi::communicator \&world, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} level)
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__mpi_a7c14e0bec9c9da1d56a348c9a0cf1f8}{cowichan\_\-mpi::power2} (\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} n)
\item 
void \hyperlink{namespacecowichan__mpi_4ab537d0df99e9011b206c7259e82d35}{cowichan\_\-mpi::quick\_\-sort} (const mpi::communicator \&world, \hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} level, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} owner)
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__mpi_83904b95f448398ff15331182ee0c007}{cowichan\_\-mpi::quick\_\-sort\_\-partition} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} pivotIndex)
\end{CompactItemize}

\subsection{Detailed Description}
Sorting algorithms that use MPI.

One algorithms is included: \begin{enumerate}
\item Parallel Quick Sort \end{enumerate}

\subsection{Define Documentation}
\hypertarget{cowichan__mpi_2sort_8hpp_b3aee1394b5864d458c40b7878acbe83}{
\index{cowichan\_\-mpi/sort.hpp@{cowichan\_\-mpi/sort.hpp}!QUICK\_\-SORT\_\-CUTOFF@{QUICK\_\-SORT\_\-CUTOFF}}
\index{QUICK\_\-SORT\_\-CUTOFF@{QUICK\_\-SORT\_\-CUTOFF}!cowichan_mpi/sort.hpp@{cowichan\_\-mpi/sort.hpp}}
\subsubsection[{QUICK\_\-SORT\_\-CUTOFF}]{\setlength{\rightskip}{0pt plus 5cm}\#define QUICK\_\-SORT\_\-CUTOFF~100}}
\label{cowichan__mpi_2sort_8hpp_b3aee1394b5864d458c40b7878acbe83}

Quick sort cutoff (becomes insertion sort) - must be $>$ 1

### 2009-08-07 doc/latex/cowichan__mpi_8hpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{cowichan__mpi_8cpp}{
\section{cowichan\_\-mpi/cowichan\_\-mpi.cpp File Reference}
\label{cowichan__mpi_8cpp}\index{cowichan\_\-mpi/cowichan\_\-mpi.cpp@{cowichan\_\-mpi/cowichan\_\-mpi.cpp}}
}
This file contains main method that drives the MPI implementation.

{\tt \#include \char`\"{}cowichan\_\-mpi.hpp\char`\"{}}\par
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__mpi}{cowichan\_\-mpi}
\begin{CompactList}\small\item\em Additional classes and functions specific to mpi implementation. \item\end{CompactList}

\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
int \hyperlink{cowichan__mpi_8cpp_0ddf1224851353fc92bfbff6f499fa97}{main} (int argc, char $\ast$argv\mbox{[}$\,$\mbox{]})
\item 
bool \hyperlink{namespacecowichan__mpi_bb7c07d8b23660efe06c7ee12d60bbdc}{cowichan\_\-mpi::get\_\-block} (const mpi::communicator \&world, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} lo, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} hi, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$start, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$end)
\item 
bool \hyperlink{namespacecowichan__mpi_413bf41c8bf73b560d1c16a8e5206e5f}{cowichan\_\-mpi::get\_\-block} (const mpi::communicator \&world, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} lo, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} hi, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$start, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$end, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} rank)
\end{CompactItemize}

\subsection{Detailed Description}
This file contains main method that drives the MPI implementation.

\subsection{Function Documentation}
\hypertarget{cowichan__mpi_8cpp_0ddf1224851353fc92bfbff6f499fa97}{
\index{cowichan\_\-mpi.cpp@{cowichan\_\-mpi.cpp}!main@{main}}
\index{main@{main}!cowichan_mpi.cpp@{cowichan\_\-mpi.cpp}}
\subsubsection[{main}]{\setlength{\rightskip}{0pt plus 5cm}int main (int {\em argc}, \/  char $\ast$ {\em argv}\mbox{[}$\,$\mbox{]})}}
\label{cowichan__mpi_8cpp_0ddf1224851353fc92bfbff6f499fa97}

Main method - creates a \hyperlink{class_cowichan_m_p_i}{CowichanMPI} instance and executes \hyperlink{class_cowichan_905f3eb45f21cdaa1c32a421d001fa4c}{Cowichan::main}. \begin{Desc}
\item[Parameters:]
\begin{description}
\item[{\em argc}]number of command line arguments. \item[{\em argv}]command line arguments. \end{description}
\end{Desc}

>>>>

\hypertarget{cowichan__mpi_8hpp}{
\section{cowichan\_\-mpi/cowichan\_\-mpi.hpp File Reference}
\label{cowichan__mpi_8hpp}\index{cowichan\_\-mpi/cowichan\_\-mpi.hpp@{cowichan\_\-mpi/cowichan\_\-mpi.hpp}}
}
Boost Message Passing Interface (MPI) implementation of \hyperlink{class_cowichan}{Cowichan} problems.

{\tt \#include \char`\"{}../cowichan/cowichan.hpp\char`\"{}}\par
{\tt \#include $<$boost/mpi.hpp$>$}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{class_cowichan_m_p_i}{CowichanMPI}
\begin{CompactList}\small\item\em Boost Message Passing Interface (MPI) implementation. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__mpi}{cowichan\_\-mpi}
\begin{CompactList}\small\item\em Additional classes and functions specific to mpi implementation. \item\end{CompactList}

\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
bool \hyperlink{namespacecowichan__mpi_bb7c07d8b23660efe06c7ee12d60bbdc}{cowichan\_\-mpi::get\_\-block} (const mpi::communicator \&world, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} lo, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} hi, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$start, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$end)
\item 
bool \hyperlink{namespacecowichan__mpi_413bf41c8bf73b560d1c16a8e5206e5f}{cowichan\_\-mpi::get\_\-block} (const mpi::communicator \&world, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} lo, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} hi, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$start, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$end, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} rank)
\item 
{\footnotesize template$<$class Archive $>$ }\\void \hyperlink{namespaceboost_1_1serialization_214544bc307816738f05752310ed7336}{boost::serialization::serialize} (Archive \&ar, \hyperlink{class_weighted_point}{WeightedPoint} \&p, const unsigned int version)
\item 
{\footnotesize template$<$class Archive $>$ }\\void \hyperlink{namespaceboost_1_1serialization_899888015920ed0de50a4ec4786a4d5d}{boost::serialization::serialize} (Archive \&ar, \hyperlink{class_point}{Point} \&p, const unsigned int version)
\end{CompactItemize}

\subsection{Detailed Description}
Boost Message Passing Interface (MPI) implementation of \hyperlink{class_cowichan}{Cowichan} problems.

### 2009-08-07 doc/latex/cowichan__openmp_2sort_8hpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{sort_8hpp}{
\section{cowichan\_\-openmp/sort.hpp File Reference}
\label{sort_8hpp}\index{cowichan\_\-openmp/sort.hpp@{cowichan\_\-openmp/sort.hpp}}
}
Sorting algorithms that use OpenMP.

@@

\end{CompactItemize}
\subsection*{Defines}
\begin{CompactItemize}
\item 
\#define \hyperlink{sort_8hpp_b3aee1394b5864d458c40b7878acbe83}{QUICK\_\-SORT\_\-CUTOFF}~100
\item 
\#define \hyperlink{sort_8hpp_66832e055934d011da279261bcfafdd1}{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}~1000
\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
void \hyperlink{namespacecowichan__openmp_9cbb3540b84f4e051f072a08c2c1d5db}{cowichan\_\-openmp::histogram\_\-sort} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len)
\item 
void \hyperlink{namespacecowichan__openmp_64208258cab6e46db879b46b40581134}{cowichan\_\-openmp::quick\_\-sort} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len)
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__openmp_2733c307de545e237e020a1f166850c5}{cowichan\_\-openmp::quick\_\-sort\_\-partition} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} pivotIndex)
\end{CompactItemize}

\label{_details}
\hypertarget{_details}{}
\subsection{Detailed Description}
Sorting algorithms that use OpenMP.

@@

\subsection{Define Documentation}
\hypertarget{sort_8hpp_b3aee1394b5864d458c40b7878acbe83}{
\index{sort.hpp@{sort.hpp}!QUICK\_\-SORT\_\-CUTOFF@{QUICK\_\-SORT\_\-CUTOFF}}
\index{QUICK\_\-SORT\_\-CUTOFF@{QUICK\_\-SORT\_\-CUTOFF}!sort.hpp@{sort.hpp}}
\subsubsection[{QUICK\_\-SORT\_\-CUTOFF}]{\setlength{\rightskip}{0pt plus 5cm}\#define QUICK\_\-SORT\_\-CUTOFF~100}}
\label{sort_8hpp_b3aee1394b5864d458c40b7878acbe83}

Quick sort cutoff (becomes insertion sort) - must be $>$ 1 \hypertarget{sort_8hpp_66832e055934d011da279261bcfafdd1}{
\index{sort.hpp@{sort.hpp}!QUICK\_\-SORT\_\-TASK\_\-CUTOFF@{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}}
\index{QUICK\_\-SORT\_\-TASK\_\-CUTOFF@{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}!sort.hpp@{sort.hpp}}
\subsubsection[{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}]{\setlength{\rightskip}{0pt plus 5cm}\#define QUICK\_\-SORT\_\-TASK\_\-CUTOFF~1000}}
\label{sort_8hpp_66832e055934d011da279261bcfafdd1}

>>>>

\hypertarget{cowichan__openmp_2sort_8hpp}{
\section{cowichan\_\-openmp/sort.hpp File Reference}
\label{cowichan__openmp_2sort_8hpp}\index{cowichan\_\-openmp/sort.hpp@{cowichan\_\-openmp/sort.hpp}}
}
Sorting algorithms that use OpenMP.

@@

\end{CompactItemize}
\subsection*{Defines}
\begin{CompactItemize}
\item 
\#define \hyperlink{cowichan__openmp_2sort_8hpp_b3aee1394b5864d458c40b7878acbe83}{QUICK\_\-SORT\_\-CUTOFF}~100
\item 
\#define \hyperlink{cowichan__openmp_2sort_8hpp_66832e055934d011da279261bcfafdd1}{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}~1000
\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
void \hyperlink{namespacecowichan__openmp_9cbb3540b84f4e051f072a08c2c1d5db}{cowichan\_\-openmp::histogram\_\-sort} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len)
\item 
void \hyperlink{namespacecowichan__openmp_64208258cab6e46db879b46b40581134}{cowichan\_\-openmp::quick\_\-sort} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len)
\item 
\hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} \hyperlink{namespacecowichan__openmp_2733c307de545e237e020a1f166850c5}{cowichan\_\-openmp::quick\_\-sort\_\-partition} (\hyperlink{class_weighted_point}{WeightedPointVector} vector, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} len, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} pivotIndex)
\end{CompactItemize}

\subsection{Detailed Description}
Sorting algorithms that use OpenMP.

@@

\subsection{Define Documentation}
\hypertarget{cowichan__openmp_2sort_8hpp_b3aee1394b5864d458c40b7878acbe83}{
\index{cowichan\_\-openmp/sort.hpp@{cowichan\_\-openmp/sort.hpp}!QUICK\_\-SORT\_\-CUTOFF@{QUICK\_\-SORT\_\-CUTOFF}}
\index{QUICK\_\-SORT\_\-CUTOFF@{QUICK\_\-SORT\_\-CUTOFF}!cowichan_openmp/sort.hpp@{cowichan\_\-openmp/sort.hpp}}
\subsubsection[{QUICK\_\-SORT\_\-CUTOFF}]{\setlength{\rightskip}{0pt plus 5cm}\#define QUICK\_\-SORT\_\-CUTOFF~100}}
\label{cowichan__openmp_2sort_8hpp_b3aee1394b5864d458c40b7878acbe83}

Quick sort cutoff (becomes insertion sort) - must be $>$ 1 \hypertarget{cowichan__openmp_2sort_8hpp_66832e055934d011da279261bcfafdd1}{
\index{cowichan\_\-openmp/sort.hpp@{cowichan\_\-openmp/sort.hpp}!QUICK\_\-SORT\_\-TASK\_\-CUTOFF@{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}}
\index{QUICK\_\-SORT\_\-TASK\_\-CUTOFF@{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}!cowichan_openmp/sort.hpp@{cowichan\_\-openmp/sort.hpp}}
\subsubsection[{QUICK\_\-SORT\_\-TASK\_\-CUTOFF}]{\setlength{\rightskip}{0pt plus 5cm}\#define QUICK\_\-SORT\_\-TASK\_\-CUTOFF~1000}}
\label{cowichan__openmp_2sort_8hpp_66832e055934d011da279261bcfafdd1}

### 2009-08-07 doc/latex/cowichan__tbb_2half_8cpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{cowichan__tbb_2gauss_8cpp}{
\section{cowichan\_\-tbb/gauss.cpp File Reference}
\label{cowichan__tbb_2gauss_8cpp}\index{cowichan\_\-tbb/gauss.cpp@{cowichan\_\-tbb/gauss.cpp}}
}
TBB gauss implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_row_elimination}{cowichan\_\-tbb::RowElimination}
\begin{CompactList}\small\item\em Performs row elimination, i.e. eliminate i-th column in j-th row. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB gauss implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_d51868e0e65482f7c9e69d73b3904822}{CowichanTBB::gauss} \end{Desc}

>>>>

\hypertarget{cowichan__tbb_2half_8cpp}{
\section{cowichan\_\-tbb/half.cpp File Reference}
\label{cowichan__tbb_2half_8cpp}\index{cowichan\_\-tbb/half.cpp@{cowichan\_\-tbb/half.cpp}}
}
TBB half implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_shuffle}{cowichan\_\-tbb::Shuffle}
\begin{CompactList}\small\item\em This class does a halving shuffle. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

@@

\subsection{Detailed Description}
TBB half implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_bbf17e641657d54fc0c571c008ac8f7a}{CowichanTBB::half} \end{Desc}

### 2009-08-07 doc/latex/cowichan__tbb_2life_8cpp.tex
Re-generated doxygen with linuxtuples additions.

\hypertarget{cowichan__tbb_2hull_8cpp}{
\section{cowichan\_\-tbb/hull.cpp File Reference}
\label{cowichan__tbb_2hull_8cpp}\index{cowichan\_\-tbb/hull.cpp@{cowichan\_\-tbb/hull.cpp}}
}
TBB hull implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_maximum_distance}{cowichan\_\-tbb::MaximumDistance}
\begin{CompactList}\small\item\em Compute maximum distance for hull. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

\end{CompactItemize}
\subsection*{Functions}
\begin{CompactItemize}
\item 
void \hyperlink{namespacecowichan__tbb_08647459098335f4d3abda9054a99547}{cowichan\_\-tbb::quickhull} (\hyperlink{class_point}{PointVector} pointsIn, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} n, \hyperlink{class_point}{PointVector} pointsOut, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$hn)
\item 
void \hyperlink{namespacecowichan__tbb_689d689bc3d950d3dd7fb9df89d4156e}{cowichan\_\-tbb::hull\_\-split} (\hyperlink{class_point}{PointVector} pointsIn, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} n, \hyperlink{class_point}{PointVector} pointsOut, \hyperlink{cowichan_8hpp_5b04577d5d21124855deaad298595371}{index\_\-t} $\ast$hn, \hyperlink{class_point}{Point} $\ast$p1, \hyperlink{class_point}{Point} $\ast$p2)
\end{CompactItemize}

\subsection{Detailed Description}
TBB hull implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_0d23aa05dc21fd9e8b033769097b4b18}{CowichanTBB::hull} \end{Desc}

>>>>

\hypertarget{cowichan__tbb_2life_8cpp}{
\section{cowichan\_\-tbb/life.cpp File Reference}
\label{cowichan__tbb_2life_8cpp}\index{cowichan\_\-tbb/life.cpp@{cowichan\_\-tbb/life.cpp}}
}
TBB life implementation.

{\tt \#include \char`\"{}cowichan\_\-tbb.hpp\char`\"{}}\par
\subsection*{Classes}
\begin{CompactItemize}
\item 
class \hyperlink{classcowichan__tbb_1_1_game_of_life}{cowichan\_\-tbb::GameOfLife}
\begin{CompactList}\small\item\em Ping-pong solution to game of life. \item\end{CompactList}\end{CompactItemize}
\subsection*{Namespaces}
\begin{CompactItemize}
\item 
namespace \hyperlink{namespacecowichan__tbb}{cowichan\_\-tbb}
\begin{CompactList}\small\item\em Additional classes and functions specific to tbb implementation. \item\end{CompactList}

\end{CompactItemize}

\subsection{Detailed Description}
TBB life implementation.

\begin{Desc}
\item[See also:]\hyperlink{class_cowichan_t_b_b_273e3e8a2e05108f59ec613472bfa363}{CowichanTBB::life} \end{Desc}
